\section{Processing note}
Each copy of your thesis or dissertation will be checked for margins, clarity of copy, and pagination. The Graduate School will run the manuscript through the Turn It In plagiarism tool. \\

Electronically submitted theses/dissertations are available in electronic format only; no hard copies will be produced. Students are responsible for binding any copies for personal use or for distribution to their advisor, department, or committee members.

\section{Dissertation \& Thesis Processing Fee}
Mandatory processing fees are required for all theses (\$85.00) and all dissertations (\$95.00). Due to COVID-19, the process has changed. Log into your Student Center in MyNEVADA. Under the Finances section, click on the link “Purchase Miscellaneous Items.” Select the applicable processing fee to pay (Dissertation or Thesis) and complete the transaction. You will receive a receipt that generates overnight.  Please keep this item as proof of payment for your records. Our office will automatically check for payment posted.

\section{Using copyrighted materials}
You must certify in ProQuest that any copyrighted material used in your work, beyond brief excerpts, is with the written permission of the copyright owner. Attach copies of permission letters to the agreement form.

\section{Copyright registration (optional)}
Students have the opportunity to register a copyright on the graduate work with the U.S. Copyright Office. It is strictly optional, and there is a \$55.00 fee associated with the service. Students submitting electronically pay online. Paying for the claim to copyright is a voluntary action, which allows a court of law to award monetary damages if the copyright is infringed. You may file a registration of copyright yourself by sending a properly completed application form, a nonrefundable filing fee of \$45.00 and a nonreturnable copy of your thesis or dissertation to the United States Copyright Office. Application materials and instructions are available from: \begin{verbatim}
Register of Copyrights 
Copyright Office 
Library of Congress 
Washington, D.C. 20559-6000 
Information is also available at the website:
http://lcweb.loc.gov/copyright/
\end{verbatim}